Articles of Association of London Hackspace Ltd.

### 2011-07-16 constitution/articles-body.tex
One Click Orgs phase one clause

\item
  \begin{enumerate}
  \item
    The directors may regulate their proceedings as they think fit,
    subject to the provisions of the articles.
  \item
    Any director may call a meeting of the directors.
  \item
    The secretary (if any) must call a meeting of the directors if
    requested to do so by a director.
  \item
    Questions arising at a meeting shall be decided by a majority of
    votes.
  \item
    In the case of an equality of votes, the person who is chairing the
    meeting shall have a second or casting vote.
  \item
    A meeting may be held by suitable electronic means agreed by the
    directors in which each participant may communicate with all the
    other participants.
  \end{enumerate}
\item
  \begin{enumerate}
  \item
    No decision may be made by a meeting of the directors unless a
    quorum is present at the time the decision is purported to be made.
    `Present' includes being present by suitable electronic means
    agreed by the directors in which a participant or participants may
    communicate with all the other participants.
  \item
    The quorum shall be two or the number nearest to one-third of the
    total number of directors, whichever is the greater, or such larger
    number as may be decided from time to time by the directors.
  \item
    A director shall not be counted in the quorum present when any
    decision is made about a matter upon which that director is not
    entitled to vote.
  \end{enumerate}
\item
  If the number of directors is less than the number fixed as the
  quorum, the continuing directors or director may act only for the
  purpose of filling vacancies or of calling a general meeting.
\item
  \begin{enumerate}
  \item
    The directors shall appoint a director to chair their meetings and
    may at any time revoke such appointment.
  \item
    If no-one has been appointed to chair meetings of the directors or
    if the person appointed is unwilling to preside or is not present
    within ten minutes after the time appointed for the meeting, the
    directors present may appoint one of their number to chair that
    meeting.
  \item
    The person appointed to chair meetings of the directors shall have
    no functions or powers except those conferred by the articles or
    delegated to him or her by the directors.
  \end{enumerate}
\item
  \begin{enumerate}
  \item
    A resolution in writing or in electronic form agreed by all of the
    directors entitled to receive notice of a meeting of the directors
    and to vote upon the resolution shall be as valid and effectual as
    if it had been passed at a meeting of the directors duly convened
    and held.
  \item
    The resolution in writing may comprise several documents containing
    the text of the resolution in like form to each of which one or
    more directors has signified their agreement.
  \end{enumerate}

>>>>

\item
  \begin{enumerate}
    \item
    The Directors may from time to time specify a web based system (``the
    Governance System'') for recording and managing their decision making process.
    \item
    The Governance System must:
        \begin{enumerate}
            \item
             permit any director to create a proposal that is then available for viewing (on
             presentation of suitable credentials) by all directors and any member of the
             Association;
            \item
            after a proposal has been created, send it promptly to each director's email address;
            \item
             maintain one or more rules as to the period (``the voting period'') within which any
             proposal must be accepted or rejected, which may vary from proposal to proposal;
            \item
             during the voting period, permit any director to indicate whether they accept or reject
             the proposal;
            \item
             record the votes cast by each director;
            \item
             record that a proposal has been ``passed'' if the requisite number of directors have
             indicated their acceptance of the proposal via the governance system;
            \item
             permit the recording of minutes; and
            \item
             maintain a current contact email address for each director (``the director's email
             address'').
        \end{enumerate}
    \item
    Any proposal that has been recorded as ``passed'' by the Governance System shall
    be treated as a decision of the directors.
    \item
    The Governance System to be used on the adoption of these articles shall be that
    supplied by One Click Orgs and accessed on the World Wide Web at the address
    http://london-gov.hackspace.org.uk
  \end{enumerate}

\item
  \begin{enumerate}
    \item
    Decisions of the directors may be made either:
    \begin{enumerate}
        \item
        by the use of the Governance System; or
        \item
        by a written resolution in accordance with the procedure described below.
    \end{enumerate}
    \item
    All directors' decisions must be made in one of these two ways, and a decision
    made in any other way will be ineffective.
    \item
    The requisite number of directors who must accept a proposal made using the
    Governance System or a written resolution before it is passed is [a majority of the
    number of directors for the time being].
  \end{enumerate}

\item
    A written resolution may be passed if:
    \begin{enumerate}
        \item
        the text of the resolution is circulated to all directors in writing; and
        \item
        the requisite number of directors have given to all the other directors in writing their
        agreement to the text of the resolution.
    \end{enumerate}
